### 2022-07-05 paper/main.tex
citations

% For the references
\usepackage[sorting=none]{biblatex}
\addbibresource{References.bib}

@@

\par Before we begin the gathering of the data, we must first understand the scale at which the data should be collected. First, we are collecting data that pertains to the United States. Second, in a general sense, we want to measure at a city-level scale. The city is the base-level at which a critical mass of population can support an online community; a city provides a geographic center and a name to associate with a community. However, the definition of a city is rather murky. The definition varies on a state-by-state basis due to the nature in which a state delineates county-level subdivisions. All states are broken down into counties, but differ in how counties are partitioned. For example, New York breaks down counties into towns, cities, and villages (REF), while North Dakota only subdivides counties into cities, with excluded areas remaining unincorporated (REF). In this way, we can think of city limits and city populations as somewhat arbitrary. There is no consistent, uniform definition, so cities should not be compared to each other. To equalize these differences, we use statistical area definitions provided by the United States Census Bureau.

@@

\par The Census Bureau provides several statistical area definitions to normalize city population and sizes. The first and most accurate definition is for Urban Areas (UAs) and Urban Clusters (UCs). UAs are dense clusters of people that house over 50,000 people. UCs are similarly measured dense clusters of people with between 2,500 and 50,000 people. UAs and UCs are computed by first identifying a dense cluster of census blocks, the smallest census geography (REF). From here, the UA or UC snakes off from the central core to include housing that fits the density requirements in less dense census blocks (REF). This process creates the ``true'' city limits, which are unaffected by municipal boundaries.

\par While Urban Areas are an effective method of measuring the true sizes of cities, they are difficult to map and obtain statistics on. Their shapes are generally compact and do not have any sort of uniform governing body. To alleviate these issues, we choose Metropolitan Statistical Areas (MSAs) as our scale. MSAs consist of the county or counties in which an Urban Area lies, alongside any counties in which 25\% of the population commutes to a core county (REF). In this way, we gain the population measurement accuracy of UAs with the ease of data access from state-defined municipalities. MSAs also lump together nearby cities, such as New York, Newark, and Jersey City, to avoid redundant analysis. As of March 2020, there are 384 Metropolitan Statistical Areas (REF), each with a corresponding Reddit community.

@@

\par When analyzing our selected Reddit communities, we need to consider the geospatial aspects of social media. There is no barrier preventing someone from, for example, Los Angeles from posting in a New York City community. (REF) measure the nature of geographic social networks. They compared the geospatial proximity of graph-connected users on four social media sites. They found that sites, such as FourSquare, that had an explicitly nature had a higher degree of locality. However, sites that focused more on general information exchanges showed less geographic clustering. The Reddit communities we are analyzing hold an interesting space between these two categories; they are both tied to place and detached from it. There is not a geographic component stopping a user from posting to a distant community, but the geospatial nature of the community itself can lead to geographic clustering.

@@

% REFS:
% https://books.google.com/books?id=BmwuDwAAQBAJ&lpg=PP1&ots=_PlVBghHER&dq=media%20and%20crime&lr&pg=PP1#v=onepage&q=media%20and%20crime&f=false
% https://doi.org/10.1177/0002716295539001011
% https://doi.org/10.1177/0002764296039004003
% https://doi.org/10.1177/19401612211020929
% https://www.cambridge.org/core/books/television-and-its-viewers/83C017F8F8416B5D5F2716EBE5D354BF
% http://personal.psu.edu/exs44/597b-Comm&Crime/Wilson-Kelling-Broken%20Windows.pdf
% https://researchgate.net/profile/Tracey-Meares-2/publication/268224149_The_Law_and_Social_Science_of_Stop_and_Frisk/links/54665ea60cf25b85d17f6112/The-Law-and-Social-Science-of-Stop-and-Frisk.pdf
% https://oxford.universitypressscholarship.com/view/10.1093/acprof:oso/9780195369083.001.0001/acprof-9780195369083
% https://policycommons.net/artifacts/1817184/news-consumption-across-social-media-in-2021/2554124/
% https://papers.ssrn.com/sol3/papers.cfm?abstract_id=2771080

\par Traditional media, such as television, newspapers, magazines, and radio, have long been intertwined with a fascination for crime. Live manhunts for people such as OJ Simpson (REF 1) and the Boston Bombers (REF ?) have captured and enthralled viewers and readers. However, while high-profile cases garner much of the attention, local and lower-profile cases often inhabit newspaper columns and television segments. It is with these cases that people grow uneasy with the sense of public safety in their community. A flurry of reporting on violent acts can increase worry, stress, and fear that crime is rising, even if the documented crime statistics show that crime has not increased (REF 3).

\par An increase in a fear of crime can have implications beyond elevated negative emotions. Fear of crime has far-reaching political social (REF 1), (REF ?), and institutional (REF 2) impacts. Belief in excessive amounts of crime can lead to loss of community cohesion (REF 3). (REF 3) found that as television news media consumption increased, distrust both in the local community and the world ``out there'' increased. Additionally, media creators often sensationalized stories, turning unfortunate incidents into grim spectacles. Those that perceived crime to be worse than others were more likely to perform excessive crime prevention actions, such as not leaving their house or engaging with the neighborhood.

\par (REF 4) describes how the prevalence of crime discussion affected the 2016 presidential election in the United States. The authors found that voters who consumed more television in turn consumed more campaign advertisements, of which many were about issues such as crime and violence. Frequent crime media consumers predict crime and violence issues to be worse than they really are (REF 5). Furthermore, the authors found that excessive crime reporting and media exposure had impacts on voting patterns; those that believed crime to be worse tended to vote for more conservative candidates.

\par Worry of crime victimization can lead to the creation of institutional policies meant to combat the perceived threat. One notable example is the idea of Broken Windows Theory (REF 6) and a practice that stemmed from its development, known as stop and frisk (REF 7). Broken Windows Theory states that visible signs of crime and disorder lead to further crimes and disorder (REF 6). Essentially, the theory states that ignoring minor criminal incidents can lead to more frequent and serious issues. Acting on this theory, the New York Police Department instituted a stop and frisk policy, in which police officers temporarily detained civilians suspected of carrying illegal objects (REF 7). The effectiveness of the policy, while believed to be effective at the time, has since come under scrutiny. Researchers found that only 6\% of stops resulted in arrests (REF 7) and that there is no clear proof that stop and frisk contributed to the decline in crime in New York City (REF 8). Stop and frisk was removed as a policy in 2013 when it was deemed unconstitutional (REF 7).

>>>>

% For the references
\usepackage[sorting=nty]{biblatex}
\addbibresource{References.bib}

@@

\par Before we begin the gathering of the data, we must first understand the scale at which the data should be collected. First, we are collecting data that pertains to the United States. Second, in a general sense, we want to measure at a city-level scale. The city is the base-level at which a critical mass of population can support an online community; a city provides a geographic center and a name to associate with a community. However, the definition of a city is rather murky. The definition varies on a state-by-state basis due to the nature in which a state delineates county-level subdivisions. All states are broken down into counties, but differ in how counties are partitioned. For example, New York breaks down counties into towns, cities, and villages, while North Dakota only subdivides counties into cities, with excluded areas remaining unincorporated. In this way, we can think of city limits and city populations as somewhat arbitrary. There is no consistent, uniform definition, so cities should not be compared to each other. To equalize these differences, we use statistical area definitions provided by the United States Census Bureau.

@@

\par The Census Bureau provides several statistical area definitions to normalize city population and sizes. The first and most accurate definition is of Urban Areas (UAs) and Urban Clusters (UCs). UAs are dense clusters of people that house over 50,000 people. UCs are similarly measured dense clusters of people with between 2,500 and 50,000 residents. UAs and UCs are computed by first identifying a dense cluster of census blocks, the smallest census geography. From here, the UA or UC snakes off from the central core to include housing that fits the density requirements in less dense census blocks \cite{censusurban}. This process creates the ``true'' city limits, which are unaffected by municipal boundaries.

\par While Urban Areas are an effective method of measuring the true sizes of cities, they are difficult to map and obtain statistics on. Their shapes are generally compact and do not have any sort of uniform governing body. To alleviate these issues, we choose Metropolitan Statistical Areas (MSAs) as our scale. MSAs consist of the county or counties in which an Urban Area lies, alongside any counties in which 25\% of the population commutes to a core county \cite{censusmetro}. In this way, we gain the population measurement accuracy of UAs with the ease of data access from state-defined municipalities. MSAs also lump together nearby cities, such as New York, Newark, and Jersey City, to avoid redundant analysis. As of March 2020, there are 384 Metropolitan Statistical Areas \cite{censusmetro}, each with a corresponding Reddit community.

@@

\par When analyzing our selected Reddit communities, we need to consider the geospatial aspects of social media. There is no barrier preventing someone from, for example, Los Angeles from posting in a New York City community. Scellato et al. measure the nature of geographic social networks \cite{sscellato}. They compared the geospatial proximity of graph-connected users on four social media sites. They found that sites, such as FourSquare, that had an explicitly geographic nature had a higher degree of locality. However, sites that focused more on general information exchanges showed less geographic clustering. The Reddit communities we are analyzing hold an interesting space between these two categories; they are both tied to place and detached from it. There is not a geographic component stopping a user from posting to a distant community, but the geospatial nature of the community itself can lead to geographic clustering.

@@

% REFS:

% https://policycommons.net/artifacts/1817184/news-consumption-across-social-media-in-2021/2554124/
% https://papers.ssrn.com/sol3/papers.cfm?abstract_id=2771080

\par Traditional media, such as television, newspapers, magazines, and radio, have long been intertwined with a fascination for crime. Live manhunts for suspects such as OJ Simpson \cite{yjewkes} and the Boston Bombers (REF ?) have captured and enthralled viewers and readers. However, while high-profile cases garner much of the attention, local and lower-profile cases often inhabit newspaper columns and television segments. It is with these cases that people grow uneasy with the sense of public safety in their community. A flurry of reporting on violent acts can increase worry, stress, and fear that crime is rising, even if the documented crime statistics show that crime has not increased \cite{lheath}.

\par An increase in a fear of crime can have implications beyond elevated negative emotions. Fear of crime has far-reaching political, social \cite{yjewkes}, and institutional \cite{vsacco} impacts. Belief in excessive amounts of crime can lead to loss of community cohesion \cite{lheath}. Heath and Gilbert found that as television news media consumption increased, distrust both in the local community and the world ``out there'' increased \cite{lheath}. Additionally, media creators often sensationalized stories, turning unfortunate incidents into grim spectacles. Those that perceived crime to be worse than others were more likely to perform excessive crime prevention actions, such as not leaving their house or engaging with the neighborhood.

\par Liu et al. describe how the prevalence of crime discussion affected the 2016 presidential election in the United States \cite{jliu}. The authors found that voters who consumed more television in turn consumed more campaign advertisements. About 15\% of campaign advertisements were about issues such as crime and violence. Frequent crime media consumers predict crime and violence issues to be worse than they really are \cite{jshanahan}. Furthermore, the authors found that excessive crime reporting and media exposure had impacts on voting patterns; those that believed crime to be worse tended to vote for more conservative candidates.

\par Worry of crime victimization can lead to the creation of institutional policies meant to combat the perceived threat. One notable example is the idea of Broken Windows Theory \cite{jwilson} and a practice that stemmed from its development, known as stop and frisk \cite{tmeares}. Broken Windows Theory states that visible signs of crime and disorder lead to further crimes and disorder \cite{jwilson}. Essentially, the theory states that ignoring minor criminal incidents can lead to more frequent and serious issues. Acting on this theory, the New York Police Department instituted a stop and frisk policy, in which police officers temporarily detained civilians suspected of carrying illegal objects \cite{tmeares}. The effectiveness of the policy, while believed to be effective at the time, has since come under scrutiny. Researchers found that only 6\% of stops resulted in arrests \cite{tmeares} and that there is no clear proof that stop and frisk contributed to the decline in crime in New York City \cite{dweisburd}. Stop and frisk was removed as a policy in 2013 when it was deemed unconstitutional \cite{tmeares}.
